Speed and Precision in Range Analysis

### 2012-07-01 doc/Manuscript/SBLP/paper.tex
Fixed some errors.

Figure~\ref{fig:wholeImpact} compares the precision of the intra and
inter-procedural analyses for the five largest programs in three different
categories of benchmarks: SPEC CPU 2006, the Stanford Suite~\footnote{\texttt{http://classes.engineering.wustl.edu/cse465/docs/BCCExamples/stanford.c}} and
Bitwise~\cite{Stephenson00}.
Our results for the SPEC programs were disappointing: on average, for
the five largest programs, the intra-procedural version of our analysis saves
5.23\% of bits per variable.
The inter-procedural version increases this number to 8.89\%.
A manual inspection of the SPEC programs reveals that this result is expected:
these programs use many external library functions, which we cannot analyze, and
their source codes do not provide enough explicit constants to power our analysis
up.
However, with numerical benchmarks we fare much better.
On average, our inter-procedural algorithm reduces the bitwidth of the
Stanford benchmarks by 36.24\%.
For Bitwise we obtain a bitwidth reduction of 12.27\%.
However, this average is lowered by two outliers: \texttt{edge\_detect} and
\texttt{sha}, which cannot be reduced.
The bitwise benchmarks were implemented by Stephenson
{\em et al.}~\cite{Stephenson00} to validate their bitwidth analysis.
Our results are on par with those found by the original authors.
The bitwise programs contain only the \texttt{main} function; thus, different
versions of our algorithm find the same results when applied onto these
programs.

>>>>

Figure~\ref{fig:wholeImpact} compares the precision of the intra and
inter-procedural analyses for the five largest programs in three different
categories of benchmarks: SPEC CPU 2006, the Stanford Suite~\footnote{\texttt{http://classes.engineering.wustl.edu/cse465/docs/BCCExamples/stanford.c}} and
Bitwise~\cite{Stephenson00}.
Our results for the SPEC programs were disappointing: on average, for
the five largest programs, the intra-procedural version of our analysis saves
5.23\% of bits per variable.
The inter-procedural version increases this number to 8.89\%.
A manual inspection of the SPEC programs reveals that this result is expected:
these programs use many external library functions, which we cannot analyze, and
their source codes do not provide enough explicit constants to power our analysis
up.
However, with numerical benchmarks we fare much better.
On average, our inter-procedural algorithm reduces the bitwidth of the
Stanford benchmarks by 36.24\%.
For Bitwise we obtain a bitwidth reduction of 12.27\%.
However, this average is lowered by two outliers: \texttt{edge\_detect} and
\texttt{sha}, which cannot be reduced.
The Bitwise benchmarks were implemented by Stephenson
{\em et al.}~\cite{Stephenson00} to validate their bitwidth analysis.
Our results are on par with those found by the original authors.
The Bitwise programs contain only the \texttt{main} function; thus, different
versions of our algorithm find the same results when applied onto these
programs.
